\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-06 cfhtlens.tex
added LvW's comments

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.  Figure~\ref{fig:filters} shows the integrands of these statistics (i.e. the weights placed on each $\ell$ scale),  for two cases, normalised to their maximum value.  The upper panel shows the integrand\footnote{Note that the lower left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
angular separation of $100'$. However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, 
the maximum $\theta$ is $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.  Finally, the lower panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   
If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

@@

We note that any future comparison of mock data with full curved sky non-Limber predictions will place requirements on the input weak lensing simulations.  Many currently work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles, these two approaches differ regardless of the box size.

>>>>

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.  Figure~\ref{fig:filters} shows the integrands of these statistics (i.e. the weights placed on each $\ell$ scale),  for two cases, normalised to their maximum value.  The right panel shows the integrand\footnote{Note that the lower left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
angular separation of $100'$. However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, 
the maximum $\theta$ is $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.  Finally, the left panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   
If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

@@

We note that any future comparison of mock data with full curved sky non-Limber predictions will place requirements on the input weak lensing simulations.  Many work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles these two approaches differ, regardless of the box size.

### 2016-12-06 theory.tex
added LvW's comments

 \begin{table}[htb]
\label{tab:Tl_nu}
\begin{center}
\begin{tabular}{ | l | l | c | c  | c |}
\hline
Case & ID & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & KSt & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber `Flat' Sky &  LF & $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & LS & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber `Flat' Sky & ELF & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & ELS & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended Standard Flat Sky & ESt & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  &  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
 \end{tabular}
 \end{center}
 \caption{Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.  $^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.} 
 \end{table}

@@

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.85\textwidth]{figures/Cl_xi_comp.pdf}
 \label{fig:Cl_xi}
 \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}, assuming a \citet{planck/cosmo:2015} cosmology and the 2D CFHTLenS redshift distribution. \emph{Lower Panels:} Deviations with respect to the extended Limber spherical sky model (ELS).    The dashed lines in the right panels show the largest angular scale used in the recent KIDS cosmic shear analysis where an Extended Standard (ESt) analysis was used.}
 \end{center}
 \end{figure}

>>>>

 \begin{table}[htb]
\begin{center}
\begin{tabular}{ | l | l | c | c  | c |}
\hline
Case & ID & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & KSt & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber `Flat' Sky &  LF & $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & LS & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber `Flat' Sky & ELF & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & ELS & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended Standard Flat Sky & ESt & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  &  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
 \end{tabular}
 \end{center}
 \caption{\label{tab:Tl_nu}Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.  $^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.} 
 \end{table}

@@

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.85\textwidth]{figures/Cl_xi_comp.pdf}
 \caption{ \label{fig:Cl_xi}\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}, assuming a \citet{planck/cosmo:2015} cosmology and the 2D CFHTLenS redshift distribution. \emph{Lower Panels:} Deviations with respect to the extended Limber spherical sky model (ELS).    The dashed lines in the right panels show the largest angular scale used in the recent KIDS cosmic shear analysis where an Extended Standard (ESt) analysis was used.}
 \end{center}
 \end{figure}
